PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-08-26 paper/sec-results.tex
added 3 references

\paragraph{Experimental measurements and process features.}
We select the single-differential distribution in either the transverse
momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
at NLO, $\mathcal{O}(\alphas^3)$. These orders make up our NLO QCD
computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
$\mathcal{O}(\alphas^2\alpha)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
EW corrections for this process
were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The size of the EW correction is comparable to the size of the PDF uncertainty,
except at large values of transverse momentum or invariant mass, where the
former becomes larger than the latter. This fact suggests that, once included in
a global fit, EW corrections can improve the accuracy of the PDFs. In comparison
to the scale uncertainty, the size of the EW corrections remains negligible:
despite the fact that the choice of factorisation and renormalisation scales
have been devised to optimise the convergence of the perturbative expansion,
NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Catani:2019hip,Catani:2020tko}, as expected in a process mostly initiated
by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,
the Monte Carlo statistical uncertainty remains negligible in comparison to the
data, PDF and scale uncertainties, and to the size of the EW correction. Our
conclusions are therefore not affected by Monte Carlo inefficiencies.

>>>>

\paragraph{Experimental measurements and process features.}
We select the single-differential distribution in either the transverse
momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
at NLO, $\mathcal{O}(\alphas^3)$. These orders make up our NLO QCD
computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
$\mathcal{O}(\alphas^2\alpha)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
EW corrections for this process
were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Denner:2016jyo,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Frederix:2018nkq,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The size of the EW correction is comparable to the size of the PDF uncertainty,
except at large values of transverse momentum or invariant mass, where the
former becomes larger than the latter. This fact suggests that, once included in
a global fit, EW corrections can improve the accuracy of the PDFs. In comparison
to the scale uncertainty, the size of the EW corrections remains negligible:
despite the fact that the choice of factorisation and renormalisation scales
have been devised to optimise the convergence of the perturbative expansion,
NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Behring:2019iiv,Catani:2019hip,Catani:2020tko,Czakon:2020qbd}, as expected in a process mostly initiated
by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,
the Monte Carlo statistical uncertainty remains negligible in comparison to the
data, PDF and scale uncertainties, and to the size of the EW correction. Our
conclusions are therefore not affected by Monte Carlo inefficiencies.
